### 2019-01-14 manuscript.tex
Update manuscript.tex

We analyzed the Demographic and Health Surveys (DHS) by USAID.  Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.  We did not analyze the newest dataset due to the lack of FGC benefits modules before this study finished for publication (checked in 09/17).

@@

\subsubsection{Measurements and Concepts}\label{measurements-and-concepts}

\jd{Is this s. about us or not? Why is it in our Methods?} The main constructs analyzing FGC practice were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} and applied in fgc studies (e.g., \{IloDarf18, PashPonn16}(more cites?). The theory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.  Here, the attitudes is constructed as women's attitudes of FGC benefits (see the list of FGC benefits at table XX in Appendix); perceived behavioral control as perception of gender awareness (i.e., women's attitudes towards domestic violence (see the list of attitudes towards domestic violence against women at table xx) and their social resources (education, and job?) (feminism and modernization?); and the perceived social pressures (subjective norms) as the community level of attitudes of FGC benefits and FGC prevalence (to reflect the convention norms of FGC under the convention theory). \cf{need comments!!!} \jd{Not sure what you're trying to do here. What do you mean by ``refer''? Seems loose.}

@@

>>>>

We analyzed the Demographic and Health Surveys (DHS) by USAID.  Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.  We did not analyze the newest dataset due to the lack of FGC benefits modules before this study finished for publication (checked in 1/09/19).

@@

\subsubsection{Measurements and Concepts}\label{measurements-and-concepts}
\cite{Rima08}*
\jd{Is this s. about us or not? Why is it in our Methods?} The main constructs analyzing FGC practice were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} and applied in fgc studies (e.g., \{IloDarf18, PashPonn16}(more cites?). The theory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.  Here, the attitudes is constructed as women's attitudes of FGC benefits (see the list of FGC benefits at table XX in Appendix); perceived behavioral control as perception of gender awareness (i.e., women's attitudes towards domestic violence (see the list of attitudes towards domestic violence against women at table xx) and their social resources (education, and job?) (feminism and modernization?); and the perceived social pressures (subjective norms) as the community level of attitudes of FGC benefits and FGC prevalence (to reflect the convention norms of FGC under the convention theory). \cf{need comments!!!} \jd{Not sure what you're trying to do here. What do you mean by ``refer''? Seems loose.}

@@

\cfcmt{feminism or women’s rights perspective:  which women?  Who are the women?  Women from the West or women from inside the fgc communities?}
